---
title: "Crime Map"
author: "Zack Larsen"
date: "6/22/2019"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}

library(tidyverse)
library(shiny)
library(pacman)

p_load(here, conflicted, jsonlite, data.table, geojsonio)

knitr::opts_chunk$set(echo = TRUE)

conflict_prefer("filter", "dplyr")

#here::here() # "/Users/zacklarsen/Zack_Master/Projects/Dataviz/R/Dataviz_dashboard"

stations <- fromJSON("https://feeds.divvybikes.com/stations/stations.json")

chi_data <- file.path("/Users/zacklarsen/Zack_Master/Datasets/Chicago")

crimes <- fread(file.path(chi_data,"Crimes_sample.csv")) %>% 
  na.omit()

ward_boundaries <- geojsonio::geojson_read(file.path(chi_data,"Boundaries_Wards.geojson"), what = "sp")

```

This R Markdown document is made interactive using Shiny. 

### Slider Example

This example allows you to use Shiny to select the number of bins for a histogram. Unlike other RMarkdown documents that knit to HTML and allow you to view them without running a server, this type of document that uses Shiny as the runtime requires you to serve the document locally.

```{r, echo=FALSE}
sliderInput("bins", "Number of bins:", 30, min = 1, max = 50)

renderPlot({
  x    = faithful[, 2]  # Old Faithful Geyser data
  bins = seq(min(x), max(x), length.out = input$bins + 1)

  # draw the histogram with the specified number of bins
  hist(x, breaks = bins, col = 'darkgray', border = 'white')
})
```


### Crime Totals By Ward, Layered By Primary Type

```{r shinymap, eval=FALSE}

ward_totals_by_type <- crimes %>% 
  select(Ward, `Primary Type`) %>% 
  group_by(Ward, `Primary Type`) %>% 
  summarise(n()) %<>% 
  rename(count = `n()`) %>% 
  dplyr::spread(key = `Primary Type`,value = count)

ward_totals_by_type[is.na(ward_totals_by_type)] <- 0

battery_totals <- setNames(ward_totals_by_type$BATTERY, as.character(ward_totals_by_type$Ward))
robbery_totals <- setNames(ward_totals_by_type$ROBBERY, as.character(ward_totals_by_type$Ward))
homicide_totals <- setNames(ward_totals_by_type$HOMICIDE, as.character(ward_totals_by_type$Ward))
assault_totals <- setNames(ward_totals_by_type$ASSAULT, as.character(ward_totals_by_type$Ward))
prostitution_totals <- setNames(ward_totals_by_type$PROSTITUTION, as.character(ward_totals_by_type$Ward))
gta_totals <- setNames(ward_totals_by_type$`MOTOR VEHICLE THEFT`, as.character(ward_totals_by_type$Ward))

ward_boundaries$battery_total <- battery_totals
ward_boundaries$robbery_total <- robbery_totals
ward_boundaries$homicide_total <- homicide_totals
ward_boundaries$assault_total <- assault_totals
ward_boundaries$prostitution_total <- prostitution_totals
ward_boundaries$gta_total <- gta_totals

get_palette <- function(category){
  colorQuantile("Reds", ward_boundaries$category, n = 10)
}

leaflet(ward_boundaries) %>%
  addTiles() %>%
  addPolygons(fillColor = ~get_palette(battery_total),
              weight = 2,
              opacity = 1,
              color = "white",
              dashArray = "3",
              fillOpacity = 0.9,
              group = "BATTERY",
              highlight = highlightOptions(
                weight = 5,
                color = "#666",
                dashArray = "",
                fillOpacity = 0.7,
                bringToFront = TRUE)) %>% 
  addPolygons(fillColor = ~get_palette(crime_total),
              weight = 2,
              opacity = 1,
              color = "white",
              dashArray = "3",
              fillOpacity = 0.9,
              group = "ROBBERY",
              highlight = highlightOptions(
                weight = 5,
                color = "#666",
                dashArray = "",
                fillOpacity = 0.7,
                bringToFront = TRUE)) %>% 
  addPolygons(fillColor = ~get_palette(crime_total),
              weight = 2,
              opacity = 1,
              color = "white",
              dashArray = "3",
              fillOpacity = 0.9,
              group = "HOMICIDE",
              highlight = highlightOptions(
                weight = 5,
                color = "#666",
                dashArray = "",
                fillOpacity = 0.7,
                bringToFront = TRUE)) %>% 
  addPolygons(fillColor = ~get_palette(crime_total),
              weight = 2,
              opacity = 1,
              color = "white",
              dashArray = "3",
              fillOpacity = 0.9,
              group = "ASSAULT",
              highlight = highlightOptions(
                weight = 5,
                color = "#666",
                dashArray = "",
                fillOpacity = 0.7,
                bringToFront = TRUE)) %>% 
  addPolygons(fillColor = ~get_palette(crime_total),
              weight = 2,
              opacity = 1,
              color = "white",
              dashArray = "3",
              fillOpacity = 0.9,
              group = "PROSTITUTION",
              highlight = highlightOptions(
                weight = 5,
                color = "#666",
                dashArray = "",
                fillOpacity = 0.7,
                bringToFront = TRUE)) %>% 
  addPolygons(fillColor = ~get_palette(crime_total),
              weight = 2,
              opacity = 1,
              color = "white",
              dashArray = "3",
              fillOpacity = 0.9,
              group = "GTA",
              highlight = highlightOptions(
                weight = 5,
                color = "#666",
                dashArray = "",
                fillOpacity = 0.7,
                bringToFront = TRUE)) %>% 

  addLayersControl(
    overlayGroups = c("BATTERY","ROBBERY","HOMICIDE","ASSAULT","PROSTITUTION","GTA"),
    options = layersControlOptions(collapsed = FALSE)
  )

```
